```{r, echo = FALSE}
knitr::opts_chunk$set(
		       collapse = TRUE,
		         comment = "#>",
		         fig.path = "README-"
			 )
```
<!-- README.md is generated from README.Rmd. Please edit that file and call `knitr::knit('README.Rmd')` within the top directory. -->


digitize : a plot digitizer in R
===============

This is a fork of [digitize](https://github.com/tpoisot/digitize), an R package to manually extract data from graphs. It has been modified to streamline extraction of multiple figures with similar structure.

## Install

You must have `devtools` installed:

```{r}
if(!require(devtools)) install.packages('devtools')
devtools::install_github("east-winds/digitize")
```


## How to use

```{r example}
library(digitize)

## make a temporary image
tmp <- tempfile()
png(tmp)
plot(rnorm(10) + 1:10, xlab="x", ylab="y",
     xlim=c(0,10),ylim=c(0,10), xaxs="i", yaxs="i")
dev.off()

## digitize figure using calibration twopoints=T and pre-specifying x-axis
#		(for example: digitizing multiple plots with same x-axis)
#   Select calibration points (e.g., bottom-left and top-right) in blue:
mydata <- digitize(tmp, x1=0, x2=10, twopoints=T)

## digitize figure using default settings
mydata <- digitize(tmp)
```

## Citation

```{r}
citation('digitize')
```

## Image Types


Works with three bitmap image formats (jpeg, png, bmp), automatically detecting the image type using package `readbitmap`.

## Earlier versions

Read a [tutorial from Luke Miller](http://lukemiller.org/index.php/2011/06/digitizing-data-from-old-plots-using-digitize/).
